Concurrent Programming with CXL

### 2020-06-09 book/paper.tex
Started implementation of continuations

def Condition(lk):
    result = dict{ .lock: lk, .waiters: bagEmpty() };
;
def wait(c):
    let lk = (^c).lock, blocked = True, cnt = bagCount((^c).waiters, nametag()):
        call bagAdd(&((^c).waiters), nametag());
        ^lk = False;
        while blocked:
            atomic:
                if (not (^lk)) and (bagCount((^c).waiters, nametag()) <= cnt):
                    ^lk = True;
                    blocked = False;
                ;
            ;
        ;
    ;
;
def notify(c):
    atomic:
        let waiters = (^c).waiters:
            if waiters != bagEmpty():
                call bagRemove(&((^c).waiters), bagChoose(waiters));
            ;
        ;
    ;
;
def notifyAll(c):
    (^c).waiters = bagEmpty();
;
\end{Verbatim}
\end{code}
\caption{Implementation of condition variables in the \texttt{synch} module.}
\label{fig:cv}
\end{figure}

>>>>

def Condition(lk):
    result = dict{ .lock: lk, .waiters: bagEmpty() };
;
def wait(c):
    let lk = (^c).lock, blocked = True, cnt = bagCount((^c).waiters, nametag()):
        call bagAdd(&((^c).waiters), nametag());
        ^lk = False;
        while blocked:
            atomic:
                if (not (^lk)) and (bagCount((^c).waiters, nametag()) <= cnt):
                    ^lk = True;
                    blocked = False;
                ;
            ;
        ;
    ;
;
def notify(c):
    let waiters = (^c).waiters:
        if waiters != bagEmpty():
            call bagRemove(&((^c).waiters), bagChoose(waiters));
        ;
    ;
;
def notifyAll(c):
    (^c).waiters = bagEmpty();
;
\end{Verbatim}
\end{code}
\caption{Implementation of condition variables in the \texttt{synch} module.}
\label{fig:cv}
\end{figure}
